\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% cv init

\begin{document}

% heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ignfer.com/}{\Large Ignacio Fernández}} & Email : \href{mailto:contact@ignfer.com}{contact@ignfer.com}\\
  \href{https://ignfer.com/}{https://www.ignfer.com} & Mobile : +598-96-562-666 \\
\end{tabular*}


% education
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {\href{https://utec.edu.uy/en/}{UTEC}}{Maldonado, Uruguay}
       {\href{https://utec.edu.uy/en/education/undergraduate-study/technologist-degree-in-computer-science/}{Technologist Degree in Computer Science};  GPA: 3.68/4.00}{Mar. 2022 -- Present}
    \resumeSubheading
      {\href{https://www.utu.edu.uy/}{UTU}}{Maldonado, Uruguay}
      {\href{https://www.utu.edu.uy/informatica/}{Bachelor of IT Technician and Software engineering}; ;  GPA: 3.33/4.00}{Mar. 2017 -- Dec. 2019}
  \resumeSubHeadingListEnd


% experience
\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {{\href{https://www.linkedin.com/company/austral-cargo/posts/?feedView=all}{Cargonet}}}{Punta del este, Uruguay}
      {Fullstack Software Engineer}{Apr. 2024 - Present}
      \resumeItemListStart
        \resumeItem{Codebase Refactoring}
          {Immersed in a complex codebase, driving improvements in code organization within 6 months. Led refactoring efforts to enhance maintainability and scalability while ensuring a seamless user experience.}
        \resumeItem{Frontend Development \& UI/UX Design}
          {Led frontend development and UI/UX design for a core internal platform used daily by over 20 non-tech-savvy team members, creating intuitive interfaces to ensure ease of use and operational success.}
        \resumeItem{Internal Tools Development}
          {Built and enhanced internal tools, including a platform managing over 2,400 quotation requests in 2024, streamlining processes from initial contact to final offer to boost team efficiency.}
        \resumeItem{Design System Creation}
          {Revamped UI for key internal tools by creating a design system and styling guidelines from scratch, ensuring consistent design across applications and simplifying future updates.}
        \resumeItem{Interactive Dashboard Development}
          {Designed and built an informative dashboard from an interactive Figma prototype, implemented using Recharts and Shadcn, enabling rapid feedback and data-driven decision-making.}
        \resumeItem{AI-Powered Solutions}
          {Researched and implemented AI solutions, building lightweight APIs to convert natural language queries into SQL, accelerating reporting and enhancing data access for the team.}
        \resumeItem{Versatile Contributions}
          {Took on diverse responsibilities, including service monitoring with Portainer, customer support, and backend development using Java, Spring Boot, and PostgreSQL, driving company growth.}
        \resumeItem{Adaptability \& Teamwork}
          {Demonstrated flexibility by contributing to help desk support, service monitoring, backend development, and R\&D projects, showcasing a team-first mindset and adaptability to new challenges.}
      \resumeItemListEnd


% projects
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Personal portfolio}
      {Personal portfolio description}
    \resumeSubItem{Buddgy}
      {Buddgy description}
  \resumeSubHeadingListEnd

% programming_skills
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Javascript, Java, Golang, Python, SQL}
     \hfill
     \textbf{Technologies}{: React, Docker, Figma, Github}
   }
 \resumeSubHeadingListEnd


% resume_end
\end{document}
